|

### 2020-12-07 manuscript/article.Rmd
WIP

---
title:  |
        | The Effect of Legislature Size on Public Spending
        | A Meta-Analysis
author: 
  - Huzeyfe Alptekin[^huzeyfe]
  - Danilo Freire[^danilo]
  - Umberto Mignozzetti[^umberto]
  - Catarina Roman[^catarina]
date: \today
thanks: "The authors thank Guilherme Duarte, Robert Myles McDonnell, and David Skarbek for their constructive feedback. We also thank Cedric Antunes, Luis Castro, Giovanna França, Julia Oriente, and Lucas Mingardi for their excellent research assistance. Replication materials are available at <https://github.com/danilofreire/distributive-politics-meta-analysis>. We kindly acknowledge funding from the São Paulo State Science Foundation (FAPESP grant number 2018/00646-1)."
abstract: "In a seminal article, @weingast1981political argue that there is a positive relationship between legislature size and inefficiency in public expenditures. Their proposition is currently known as the law of $1/n$ and has been widely debated in political science and public administration. However, recent studies have questioned the validity of the theory. In this letter, we estimate the first meta-analysis of the relationship between the number of legislators and public spending. Based on a sample of 29 articles, we find only mixed evidence for the effect of legislature size on government budgets. Yet the aggregate results mask important differences. While earlier, non-causal studies provide moderate support for the law of $1/n$, recent papers using causal inference methods consistently find a negative relation between seats and spending, suggesting that previous results might have been driven by spurious correlations or omitted variable bias. The available evidence also indicates that XXXXXXXXXXXXXXXX"
abstractspacing: onehalf
keywords: distributive politics; law of $1/n$; legislature size; meta-analysis; public spending
jelcodes: H21; H23; H50; H61
fontsize: 12pt
margin: 2cm
urlcolor: darkblue
linkcolor: Mahogany
citecolor: Mahogany
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    keep_tex: no
    toc: no
    toc_depth: 3
    template: article-template.latex
    md_extensions: +raw_attribute
---

@@

Over the past decades, a large literature has examined the relationship between
legislature size and public expenditure. @weingast1981political provided the
general framework to analyse distributive politics. The authors argue that the
larger the number of legislative districts ($n$), the smaller the share of tax
burden each one will bear ($1/n$), thus legislators have an incentive to
overspend in their districts and transfer the costs to the entire polity. The
first studies that assessed the "law of $1/n$", as the theory is currently
known, mostly found a positive correlation between government spending and the
number of legislature seats, although the effect was sometimes limited to the
lower house [e.g., @baqir1999districts; @bradbury2001legislative;
@gilligan1995deviations]. However, recent studies have questioned the validity
of the theory. For instance, spending limits or strong executives may reduce
the inefficiency of pork barrel projects [@chen_malhotra_2007; @primo2006stop].
Moreover, @primo2008distributive affirm that, due to spatial spillovers, a
collection of small districts can supply public goods more efficiently than the
central government. The authors conclude that a "reverse law of $1/n$" may
hold, wherein a higher number of legislators in small constituencies decrease
the overall public spending.

Our survey of the scholarship confirms this continuum of positive,
insignificant, and negative results. Out of the `r dim(dat)[1]` coefficients included in our
article sample, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 0)[which(names(prop.table(table(dat$scoefnd)))=='Positive Significant')])`\% of them are positive and statistically significant, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 0)[which(names(prop.table(table(dat$scoefnd)))=='Positive Insignificant')])`\%
are positive and statistically insignificant, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 0)[which(names(prop.table(table(dat$scoefnd)))=='Negative Insignificant')])`\% are negative and
statistically insignificant, and `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 0)[which(names(prop.table(table(dat$scoefnd)))=='Negative Significant')])`\% are negative and statistically
significant. Given this diversity of empirical findings, a systematic review of
the existing evidence may help us reach a meaningful conclusion about the effect
of legislature size on public spending. Meta-analysis is the most appropriate
method for this task. Meta-analysis combines the outcomes of multiple studies
into a single estimation and allows scholars to draw robust conclusions from the
aggregated data \citep{cooper2019handbook,hedges1985statistical}. It can also
identify potential sources of study heterogeneity, enabling researchers to
assess threats to external validity and direct future efforts into more
promising areas of academic inquiry [@doucouliagos2008democracy].

@@

Aggregate results show that council size has no significant impact on public
spending. However, the meta-regressions suggest that our study sample has high
levels of heterogeneity, and effects differ substantially according to the
study design. We find that a reliable predictor of effect size is the research
method employed in the original paper. While earlier studies that employed
conventional linear regressions often find a positive relation between
legislature size and government budgets, recent studies that use new methods of
causal inference, specially those with regression discontinuity designs,
provide consistent evidence for a negative relation. This goes in contrast with
the original theory and supports the existence of a "reverse law of $1/n$".

@@

\footnotesize
\begin{longtable}{>{\raggedright\arraybackslash}p{2.9cm}>{\raggedright\arraybackslash}p{4.5cm}>{\centering\arraybackslash}p{1.3cm}>{\centering\arraybackslash}p{1cm}>{\centering\arraybackslash}p{1cm}>{\centering\arraybackslash}p{1.4cm}>{\centering\arraybackslash}p{2.4cm}}
\caption{Papers included in the meta-analysis, listed year of appearance}\\
\toprule
\raggedright Author(s) & \centering Title & \centering Journal & \centering Year & \centering Country & \centering Method & \raggedleft Electoral System
\tabularnewline
\midrule
\endhead
```{r, echo = FALSE, results = 'asis'}
build_nams <- function(x) {
  x_ <- unlist(strsplit(as.character(x), ' & ', fixed = T, useBytes = T))
  if(length(x_) == 1) return(x_)
  else {
    aux <- x_[1]
      for (i in 2:length(x_))
        if (i == length(x_)){
          aux <- paste(aux, ' \\& \\\\ ', x_[i], sep = '')
        } else {
          aux <- paste(aux, ',\\\\ ', x_[i], sep = '')
        }
  }
  return(paste('\\begin{tabular}[t]{@{}l@{}}', aux,'\\end{tabular}', 
                   sep = ''))
}
aux <- dat %>%
  select(authorCite, title, journalCode, year, locationISO, method, elecsys3) %>%
  unique() %>%
  arrange(year)
for (i in 1:dim(aux)[1]) {
  cat(paste(build_nams(aux$authorCite[i]), ' & ', aux$title[i], ' & ',
      aux$journalCode[i], ' & ', aux$year[i], ' & ', 
      aux$locationISO[i], ' & ', aux$method[i], ' & ', 
      aux$elecsys3[i], ' \\\\ [0.5ex]', sep = ''), '\n')
}
```
\bottomrule
\label{tab:papers}
\begin{minipage}{\textwidth}
\renewcommand{\footnoterule}{}
\vspace{-0.5cm}
\footnotetext{\textbf{Note:} Unpub$=$Unpublished, JPE$=$Journal of Political
Economy, EJPE$=$European Journal of Political Economy, PC$=$Public Choice,
JPubE$=$Journal of Public Economics, JPriE$=$Journal of Private Enterprise,
APSR$=$American Political Science Review, SEJ$=$Southern Economic Journal,
UAR$=$Urban Affairs Review, SCID$=$Studies in Comparative International
Development, SSQ$=$Social Science Quarterly, SPPQ$=$State Politics and Policy
Quarterly, CPS$=$Comparative Political Studies, RivPE$=$Rivista di Politica
Economica, E\&P$=$Economics and Politics, NTJ$=$National Tax Journal,
OLS$=$Ordinary least squares, IV$=$Instrumental variables, Panel$=$Panel
data/fixed effects, RDD$=$Regression discontinuity design, M$=$Majoritarian,
NM$=$Non-majoritarian (mixed or proportional representation). Country codes
follow the ISO 3166-1 alpha-3 international standard.} \end{minipage}
\end{longtable}

@@

Our study sample reflects the development of the literature. Although the "law
of $1/n$" was first formulated in 1981, the empirical assessment of the theory
only started a few years later, as dates of publishing range from `r min(dat$year)` to `r max(dat$year)`.

Most studies focus on the United States (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='USA')])`), but our sample also contains
papers on Australia (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='AUS')])`), Brazil (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='BRA')])`), Germany (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='DEU')])`), Indonesia (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='IDN')])`), Italy (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='ITA')])`), and
Switzerland (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='CHE')])`). Five articles use cross-national data and analyse from 2 to 110
countries.

@@

res <- export2latex(
  descrTable(~.-usemeta2, aux, y = aux$usemeta2,
             show.p.overall = F, show.all = T, all.last = T), 
  caption = 'Descriptive Statistics of Moderators\\label{tab:descriptive}'
)
res <- gsub(pattern = '\\[ALL\\]', 'All Coefficients', res$desc, useBytes = T)
cat(res)
```

@@

The binomial z-test evaluates whether the coefficient of our independent
variables are positive or negative. The null hypothesis here states that the
sign of the coefficient is equally likely to be positive or negative. We start
with $n$, lower house size. Our results indicate that there is no correlation
between the number of legislators in the lower house and public expenditure 
(successes = `r as.numeric(binN$statistic)`, trials = `r as.numeric(binN$parameter)`, $p_{success} = $ `r round(as.numeric(binN$estimate), 3)`, 95\% CI = [`r round(as.numeric(binN$conf.int[1]), 3)`; `r round(as.numeric(binN$conf.int[2]), 3)`],
$p$-value = `r round(as.numeric(binN$p.value), 3)`). Note that the "law of $1/n$" suggests that there is a positive
association between both. The binomial test for log($n$) also shows a
non-statistically significant result (successes = `r as.numeric(binlogN$statistic)`, trials = `r as.numeric(binlogN$parameter)`, $p_{success} = $ `r round(as.numeric(binlogN$estimate), 3)`, 95\% CI = [`r round(as.numeric(binlogN$conf.int[1]), 3)`; `r round(as.numeric(binlogN$conf.int[2]), 3)`],
$p$-value = `r round(as.numeric(binlogN$p.value), 3)`). In contrast, we find a
positive result for the number of legislators in the upper house ($k$), which is
in line with the mainstream literature (successes = `r as.numeric(binK$statistic)`, trials = `r as.numeric(binK$parameter)`, $p_{success} = $ `r round(as.numeric(binK$estimate), 3)`, 95\% CI = [`r round(as.numeric(binK$conf.int[1]), 3)`; `r round(as.numeric(binK$conf.int[2]), 3)`],
$p$-value = `r round(as.numeric(binK$p.value), 3)`).

@@

The first column of the graph reports the results for $n$, lower chamber size.
In the first model, which correlates $n$ and expenditure per capita, we find a
standardised mean difference (SMD) of `r round(mod[[1]]$TE.random,3)` and a standard error of `r round(mod[[1]]$seTE.random,3)`
(studies = `r mod[[1]]$k`, 95\% CI = [`r round(mod[[1]]$lower.random,3)`; `r round(mod[[1]]$upper.random,3)`], $p$-value = `r round(mod[[1]]$pval.random,3)` , prediction interval
= [`r round(mod[[1]]$lower.predict,3)`; `r round(mod[[1]]$upper.predict,3)`]). Therefore, we cannot reject the null hypothesis that the
effect size is zero. The $I^2$ statistic, which quantifies the degree of
heterogeneity among studies, is equal to `r round(mod[[1]]$I2*100, 2)`\%. $I^2$ values above 75\%
indicate very high study heterogeneity \citep{higgins2019cochrane}.

@@

\begin{landscape}
\begin{figure}[p]
\begin{center}
\caption{Forest Plots for the Relationship between Legislature Size and Government Spending (Reduced Sample)}
\vspace{.3cm}
\includegraphics[width=25cm,height=17cm]{../graphs/graph1.pdf}
\label{fig:plots}
\end{center}
\end{figure}
\end{landscape}

@@

The third set of models uses $k$, upper house size, as the main independent
variable. We find a positive correlation between $k$ and expenditure per capita
and the coefficient is significant at a 10\% level (studies = `r mod[[2]]$k`, SMD = `r round(mod[[2]]$TE.random,3)`, SE
= `r round(mod[[2]]$seTE.random,3)`, 95\% CI = [`r round(mod[[2]]$lower.random,3)`; `r round(mod[[2]]$upper.random,3)`], $p$-value = `r round(mod[[2]]$pval.random,3)`, prediction interval =
[`r round(mod[[2]]$lower.predict,3)`; `r round(mod[[2]]$upper.predict,3)`], $I^2$ = `r round(mod[[2]]$I2*100, 2)`\%). But as with the other models, the prediction
interval again includes zero. When we run the same analysis in the extended
sample, we also see a significant coefficient yet a prediction interval that
contains zero (coefficients = `r mod[[9]]$k`, SMD = `r round(mod[[9]]$TE.random,3)`, SE = `r round(mod[[9]]$seTE.random,3)`, 95\% CI = [`r round(mod[[9]]$lower.random,3)`; `r round(mod[[9]]$upper.random,3)`],
$p$-value $<$ 0.001, prediction interval = [`r round(mod[[9]]$lower.predict,3)`; `r round(mod[[9]]$upper.predict,3)`], $I^2$ = `r round(mod[[9]]$I2*100, 2)`\%).

@@

In a nutshell, we find only weak evidence in favour of the "law of $1/n$".
While some models do show a positive and statistically significant result, none
of the prediction intervals are totally positive or negative. The studies also
have considerable heterogeneity, what indicates that the original coefficients
do not point consistently towards the same direction.

One reason why we have not detected any effects may be the identification strategy used to estimate the effects. On the one hand, OLS and Panel data models, require too many controls to make units comparable. On the other hand, these techniques are not as credible to estimate the causal effect of legislature size on public expenditures. Estimation methods such as Instrumental Variables, and Regression Discontinuity Design make the units comparable by employing natural and quasi-natural experiments. Figure \ref{fig:plots2} disentangle the estimation techniques for two models that there is broadly variation in the estimation method used: Lower House Size and Expenditure Per Capita (left) and Lower House Size and Log of Expenditure Per Capita (right).[XXXX DANILO CHECAR]

\begin{figure}[htb!]
\begin{center}
\caption{Forest Plots for the Relationship between Legislature Size and Government Spending with Regression Method Heterogeneity (Restricted Sample)}
\vspace{.3cm}
\includegraphics[width=1\linewidth]{../graphs/graph2.pdf}
\label{fig:plots2}
\end{center}
\end{figure}

Instrumental variables has an interesting variation: from the four coefficients listed, two are positive and two are negative. Two of these four coefficients are significant, again one positive and one negative. The subgroup analysis present a SMD negative but insignificant. When using Regression discontinuity design, the results are uniformily negative. From three papers employing the technique on the natural logarithm of expenditure per capita, all find negative and significant effects. The number of studies, only three, is not enough to predict an overall negative result, but they point in the direction that better identification suggests a zero-to-negative impact of legislature size on expenditure, in support of the reverse "law of $1/n$".[XXXX DANILO CHECAR]

@@

In this section, we run a series of meta-regressions with five covariates that may
account for differences across the selected papers. The first variable indicates
whether the study uses $n$, log($n$) or $k$ as its main explanatory variable.
The second variable shows the study publication year, which we included to
capture temporal variation in the study coefficients. We also add a dummy
variable to assess whether published articles report effect sizes that are
higher or lower than those from working papers. The fourth variable measures
whether studies focusing on non-majoritarian electoral systems report
coefficients that are smaller or larger than those from majoritarian countries.
Our last covariate is a categorical variable indicating the statistical
procedure used in the original models (panel data, instrumental variables,
OLS, or regression discontinuity design).

@@

The first two models show the results for public expenditure per capita. In both
the restricted and the extended samples, we find that models that use $n$ as an
independent variable tend to detect significantly smaller effects when compared
to $k$. This suggests that an additional member in the lower house has a smaller
impact on public spending than a member in the upper house. Moreover, the
results for the extended sample point out that recent studies find larger
effects than older ones, and that changing the electoral rules from majoritarian
to non-majoritarian increases the effects of legislature size on per capita
expenditure.

The third and fourth columns use the logarithm of expenditure per capita as the
dependent variable. No covariate is statistically significant in our smaller
sample, but two moderators are negatively associated with the outcome in our
larger study pool. They both refer to estimation methods. Studies that employ
panel/fixed effects or regression discontinuity designs (RDDs) have lower
coefficients for log expenditure per capita if we take OLS as the reference
category.

>>>>

---
title:  |
        | The Effect of Legislature Size on Public Spending
        | A Meta-Analysis
author: 
  - Huzeyfe Alptekin[^huzeyfe]
  - Danilo Freire[^danilo]
  - Umberto Mignozzetti[^umberto]
  - Catarina Roman[^catarina]
date: \today
thanks: "The authors thank Guilherme Duarte, Robert Myles McDonnell, and David Skarbek for their constructive feedback. We also thank Cedric Antunes, Luis Castro, Giovanna França, Julia Oriente, and Lucas Mingardi for their excellent research assistance. Replication materials are available at <https://github.com/danilofreire/distributive-politics-meta-analysis>. We kindly acknowledge funding from the São Paulo State Science Foundation (FAPESP grant number 2018/00646-1)."
abstract: "In a seminal article, @weingast1981political argue that there is a positive relationship between legislature size and inefficiency in public expenditures. Their proposition is currently known as the law of $1/n$ and has been widely debated in political science and public administration. However, recent studies have questioned the validity of the theory. In this letter, we estimate the first meta-analysis of the relationship between the number of legislators and public spending. Based on a sample of 29 articles, we find only mixed evidence for the effect of legislature size on government budgets. Yet the aggregate results mask important differences. While earlier, non-causal studies provide moderate support for the law of $1/n$, recent papers using causal inference methods consistently find a negative relation between seats and spending, suggesting that previous results might have been driven by spurious correlations or omitted variable bias. The available evidence also indicates that XXXXXXXXXXXXXXXX"
abstractspacing: double
keywords: distributive politics; law of $1/n$; legislature size; meta-analysis; public spending
jelcodes: H21; H23; H50; H61
fontsize: 11pt
margin: 2cm
urlcolor: darkblue
linkcolor: Mahogany
citecolor: Mahogany
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    keep_tex: no
    toc: no
    toc_depth: 3
    template: article-template.latex
    md_extensions: +raw_attribute
---

@@

Over the past decades, a large literature has examined the relationship between
legislature size and public expenditure. @weingast1981political provided the
general framework to analyse distributive politics. The authors argue that the
larger the number of legislative districts ($n$), the smaller the share of tax
burden each one will bear ($1/n$), thus legislators have an incentive to
overspend in their districts and transfer the costs to the entire polity. Most
early studies that empirically tested the "law of $1/n$", as the theory is
currently known, indeed found a positive correlation between the number of
legislature seats and different measures of government spending, although the
effect was often limited to one house [e.g., @baqir2002districting;
@gilligan1995deviations; @gilligan2001fiscal]. Recent research has further
questioned the validity of the "law of $1/n$". For instance, spending limits,
bicameralism, or strong executives may reduce the inefficiency of pork barrel
projects [@bradbury2001legislative; @chen_malhotra_2007; @primo2006stop].
Moreover, @primo2008distributive affirm that, due to spatial spillovers, a
collection of small districts can supply public goods more efficiently than the
central government. The authors conclude that a "reverse law of $1/n$" may hold,
wherein a higher number of legislators in small constituencies decrease the
overall public spending.

Our survey of the scholarship confirms this continuum of positive,
insignificant, and negative results. Out of the `r dim(dat)[1]` coefficients
included in our article sample, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Positive Significant')])`\% of
them are positive and statistically significant, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Positive Insignificant')])`\%
are positive and statistically insignificant, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Negative Insignificant')])`\%
are negative and statistically insignificant, and `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Negative Significant')])`\% are
negative and statistically significant. Given this diversity of empirical
findings, a systematic review of the existing evidence may help us reach a
meaningful conclusion about the effect of legislature size on public spending.
Meta-analysis is the most appropriate method for this task. Meta-analysis
combines the outcomes of multiple studies into a single estimation and allows
scholars to draw robust conclusions from the aggregated data
[@cooper2019handbook; @hedges1985statistical]. It can also identify potential
sources of study heterogeneity, enabling researchers to assess threats to
external validity and direct future efforts into more promising areas of
academic inquiry [@doucouliagos2008democracy].

@@

Aggregate results show that legislative size has no significant impact on public
spending. However, the meta-regressions suggest that our study sample has high
levels of heterogeneity, and effects differ substantially according to study
specifications. A reliable predictor of effect size is the research method
employed in the original paper. While papers that employ conventional linear
regressions often find a positive relation between legislature size and
government budgets, recent studies using new methods of causal inference,
specially those with regression discontinuity designs, provide consistent
evidence for a negative relation. This goes in contrast with the original theory
and supports the existence of a "reverse law of $1/n$". Additionally, we find
that non-majoritarian voting systems decrease government spending as a
percentage of GDP, which is also evidence against the "law of $1/n$". In
summary, we do not find support for the theory as originally conceived, and
causal inference models suggest that larger legislatures are associated with
lower public spending.

@@

\footnotesize
\begin{longtable}{>{\raggedright\arraybackslash}p{2.9cm}>{\raggedright\arraybackslash}p{4.5cm}>{\centering\arraybackslash}p{1.3cm}>{\centering\arraybackslash}p{1cm}>{\centering\arraybackslash}p{1cm}>{\centering\arraybackslash}p{1.4cm}>{\centering\arraybackslash}p{2.4cm}}
\caption{Papers included in the meta-analysis, ordered by year of appearance}\\
\toprule
\raggedright Author(s) & \centering Title & \centering Journal & \centering Year & \centering Country & \centering Method & \raggedleft Electoral System
\tabularnewline
\midrule
\endhead
```{r, echo = FALSE, results = 'asis', cache = T}
build_nams <- function(x) {
  x_ <- unlist(strsplit(as.character(x), ' & ', fixed = T, useBytes = T))
  if(length(x_) == 1) return(x_)
  else {
    aux <- x_[1]
      for (i in 2:length(x_))
        if (i == length(x_)){
          aux <- paste(aux, ' \\& \\\\ ', x_[i], sep = '')
        } else {
          aux <- paste(aux, ',\\\\ ', x_[i], sep = '')
        }
  }
  return(paste('\\begin{tabular}[t]{@{}l@{}}', aux,'\\end{tabular}', 
                   sep = ''))
}
aux <- dat %>%
  select(authorCite, title, journalCode, year, locationISO, method, elecsys3) %>%
  unique() %>%
  arrange(year)
for (i in 1:dim(aux)[1]) {
  cat(paste(build_nams(aux$authorCite[i]), ' & ', aux$title[i], ' & ',
      aux$journalCode[i], ' & ', aux$year[i], ' & ', 
      aux$locationISO[i], ' & ', aux$method[i], ' & ', 
      aux$elecsys3[i], ' \\\\ [0.5ex]', sep = ''), '\n')
}
```
\bottomrule
\label{tab:papers}
\begin{minipage}{\textwidth}
\renewcommand{\footnoterule}{}
\vspace{-0.5cm}
\footnotetext{\textbf{Note:} Unpub$=$Unpublished, JPE$=$Journal of Political
Economy, EJPE$=$European Journal of Political Economy, PC$=$Public Choice,
JPubE$=$Journal of Public Economics, JPriE$=$Journal of Private Enterprise,
APSR$=$American Political Science Review, SEJ$=$Southern Economic Journal,
UAR$=$Urban Affairs Review, SCID$=$Studies in Comparative International
Development, SSQ$=$Social Science Quarterly, SPPQ$=$State Politics and Policy
Quarterly, CPS$=$Comparative Political Studies, RivPE$=$Rivista di Politica
Economica, E\&P$=$Economics and Politics, NTJ$=$National Tax Journal,
OLS$=$Ordinary least squares, IV$=$Instrumental variables, Panel$=$Panel
data/fixed effects, RDD$=$Regression discontinuity design, M$=$Majoritarian,
NM$=$Non-majoritarian (mixed or proportional representation). Country codes
follow the ISO 3166-1 alpha-3 international standard.} \end{minipage}
\end{longtable}

@@

Our study sample reflects the development of the literature. Although the "law
of $1/n$" was first formulated in 1981, the empirical assessment of the theory
only started a few years later, as dates of publishing range from `r min(dat$year)`
to `r max(dat$year)`. Most studies focus on the United States (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='USA')])`), but our sample also contains
papers on Australia (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='AUS')])`), Brazil (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='BRA')])`), Germany (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='DEU')])`), Indonesia (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='IDN')])`), Italy (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='ITA')])`), and
Switzerland (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='CHE')])`). Five articles use cross-national data and analyse from 2 to 110
countries. Early studies employed OLS and panel data methods to analyse the
results, whereas the use of regression discontinuity designs is a recent
addition to the literature, starting in 2012.

@@

res <- export2latex(
  descrTable(~.-usemeta2, aux, y = aux$usemeta2,
             show.p.overall = F, show.all = T, all.last = T), 
  caption = 'Descriptive statistics of moderators\\label{tab:descriptive}'
)
res <- gsub(pattern = '\\[ALL\\]', 'All Coefficients', res$desc, useBytes = T)
cat(res)
```

@@

The binomial z-test evaluates whether the coefficient of our independent
variables are positive or negative. The null hypothesis here states that the
sign of the coefficient is equally likely to be positive or negative. We start
with $n$, lower house size. Our results indicate that there is no correlation
between the number of legislators in the lower house and public expenditure 
(successes = `r as.numeric(binN$statistic)`, trials = `r as.numeric(binN$parameter)`, p~success~ = `r round(as.numeric(binN$estimate), 3)`, 95\% CI = [`r round(as.numeric(binN$conf.int[1]), 3)`; `r round(as.numeric(binN$conf.int[2]), 3)`],
$p$-value = `r round(as.numeric(binN$p.value), 3)`). Note that the "law of $1/n$" suggests that there is a positive
association between both. The binomial test for log($n$) also shows a
non-statistically significant result (successes = `r as.numeric(binlogN$statistic)`, trials = `r as.numeric(binlogN$parameter)`, p~success~ = `r round(as.numeric(binlogN$estimate), 3)`, 95\% CI = [`r round(as.numeric(binlogN$conf.int[1]), 3)`; `r round(as.numeric(binlogN$conf.int[2]), 3)`],
$p$-value = `r round(as.numeric(binlogN$p.value), 3)`). In contrast, we find a
positive result for the number of legislators in the upper house ($k$), which is
in line with the mainstream literature (successes = `r as.numeric(binK$statistic)`, trials = `r as.numeric(binK$parameter)`, p~success~ = `r round(as.numeric(binK$estimate), 3)`, 95\% CI = [`r round(as.numeric(binK$conf.int[1]), 3)`; `r round(as.numeric(binK$conf.int[2]), 3)`],
$p$-value = `r round(as.numeric(binK$p.value), 3)`).

@@

The first column of the graph reports the results for $n$, lower chamber size.
In the first model, which correlates $n$ and expenditure per capita, we find a
standardised mean difference (SMD) of `r round(mod[[1]]$TE.random,3)` and a standard error of `r round(mod[[1]]$seTE.random,3)`
(studies = `r mod[[1]]$k`, 95\% CI = [`r round(mod[[1]]$lower.random,3)`; `r round(mod[[1]]$upper.random,3)`], $p$-value = `r round(mod[[1]]$pval.random,3)` , prediction interval
= [`r round(mod[[1]]$lower.predict,3)`; `r round(mod[[1]]$upper.predict,3)`]). Therefore, we cannot reject the null hypothesis that the
effect size is zero. The $I^2$ statistic, which quantifies the degree of
heterogeneity among studies, is equal to `r round(mod[[1]]$I2*100, 2)`\%. $I^2$ values above 75\%
indicate very high study heterogeneity [@higgins2019cochrane].

@@

\begin{landscape}
\begin{figure}[p]
\begin{center}
\caption{Forest plots of the relationship between legislature size and government spending (reduced sample)}
\vspace{.3cm}
\includegraphics[width=25cm,height=17cm]{../graphs/graph1.pdf}
\label{fig:plots}
\end{center}
\end{figure}
\end{landscape}

@@

The third set of models uses $k$, upper house size, as the main independent
variable. We find a positive correlation between $k$ and expenditure per capita
but the coefficient is not significant (studies = `r mod[[2]]$k`, SMD = `r round(mod[[2]]$TE.random,3)`, SE
= `r round(mod[[2]]$seTE.random,3)`, 95\% CI = [`r round(mod[[2]]$lower.random,3)`; `r round(mod[[2]]$upper.random,3)`], $p$-value = `r round(mod[[2]]$pval.random,3)`, prediction interval =
[`r round(mod[[2]]$lower.predict,3)`; `r round(mod[[2]]$upper.predict,3)`], $I^2$ = `r round(mod[[2]]$I2*100, 2)`\%). But as with the other models, the prediction
interval again includes zero. When we run the same analysis in the extended
sample, we see a significant coefficient for the estimate, yet the prediction interval also
contains zero (coefficients = `r mod[[9]]$k`, SMD = `r round(mod[[9]]$TE.random,3)`, SE = `r round(mod[[9]]$seTE.random,3)`, 95\% CI = [`r round(mod[[9]]$lower.random,3)`; `r round(mod[[9]]$upper.random,3)`],
$p$-value $<$ 0.001, prediction interval = [`r round(mod[[9]]$lower.predict,3)`; `r round(mod[[9]]$upper.predict,3)`], $I^2$ = `r round(mod[[9]]$I2*100, 2)`\%).

@@

In a nutshell, we find no robust evidence in favour of the "law of $1/n$".
While some models do show a positive and statistically significant result, none
of the prediction intervals are totally positive or negative. The studies also
have considerable heterogeneity, what indicates that the original coefficients
do not point consistently towards the same direction.

One reason why we have not detected any strong effects may be due to the
identification strategy authors use in their models. On the one hand, OLS and
panel data models require too many controls to make units comparable, and they
are also vulnerable to omitted variable bias or post-treatment bias
[@cinelli2020making; @pearl2015conditioning]. On the other hand, estimation
methods such as instrumental variables and, in particular, regression
discontinuity designs have become popular because of their internal validity
[@angrist2008mostly]. Figure \ref{fig:plots2} shows the disaggregated effects for
two sets of models that employ causal estimation techniques. They measure the
impact of lower house size on expenditure per capita (left) and on the natural
logarithm of expenditure per capita (right).

\begin{figure}[htb!]
\begin{center}
\caption{Forest plots of the relationship between legislature size and government spending with regression method heterogeneity (restricted sample)}
\vspace{.3cm}
\includegraphics[width=1\linewidth]{../graphs/graph2.pdf}
\label{fig:plots2}
\end{center}
\end{figure}

Papers that employed instrumental variables show an interesting variation: out
of the four coefficients listed, two are positive and two are negative. Two of
these four coefficients are significant, again one positive and one negative.
The subgroup analysis presents a SMD which is negative but insignificant. In
contrast, all papers that use regression discontinuity designs show negative and
statistically significant results. Since only three papers in our sample use
RDDs, we are cautious about predicting an overall negative relation, but they do
indicate that better identification strategies yield a zero-to-negative impact
of legislature size on expenditure, in support of the reverse "law of $1/n$".

@@

In this section, we run a series of meta-regressions with covariates that may
account for differences across the selected papers. The first variable indicates
whether the study uses $n$, log($n$) or $k$ as its main explanatory variable.
The second variable shows the study publication year, which we included to
capture temporal variation in the study coefficients. We also add a dummy
variable to assess whether published articles report effect sizes that are
higher or lower than those from working papers. The fourth variable measures
whether studies focusing on non-majoritarian electoral systems report
coefficients that are smaller or larger than those from majoritarian countries.
Our last covariate is a categorical variable indicating the statistical
procedure used in the original models (panel data, instrumental variables,
OLS, or regression discontinuity design).

@@

The first two models show the results for public expenditure per capita. No
variable reaches conventional levels of statistical significance in the
restricted sample. In the extended sample, we find that models that use $n$ as
an independent variable tend to detect significantly smaller effects when
compared to $k$. This suggests that an additional member in the lower house has
a smaller impact on public spending than a member in the upper house. Moreover,
the results for the extended sample point out that recent studies find larger
effects than older ones.

The third and fourth columns use the natural logarithm of expenditure per capita
as the dependent variable. None of the covariates are statistically significant in our
smaller sample, but two moderators are negatively associated with the outcome in
our larger study pool. They both refer to estimation methods. Studies that
employ panel/fixed effects or regression discontinuity designs (RDDs) have lower
coefficients for log expenditure per capita if we take OLS as the reference
category.

Two variables are statistically significant in the last set of
meta-regressions, which include public expenditures as a percentage
of GDP as the dependent variable. Both in our restricted and in our extended
samples, we see that newer studies have smaller coefficients than early ones,

studies with $n$ as an
independent variable have lower coefficients than those that analyse $k$, what
is consistent with our previous models. Both models also show that unpublished
papers tend to have higher coefficients than published papers. Regarding the
electoral systems, see that passing from majoritarian to non-majoritarian
decrease overall levels of public spending. Finally, we find that models
estimated with panel data have larger values than those modelled with OLS.
